---
title: "Analysis"
execute:
  echo: false
---

```{r}
#| include: false
library(targets)
library(here)
library(dplyr)
library(ggplot2)
library(tidyr)
library(sandwich)

source(here("analysis", "R", "regress.R"))

tar_config_set(store = here("_targets"))
tar_load(clg_dev)
tar_load(clg_codebook)

# Derived variables (NA treated as 0 for binary indicators)
flag <- function(x) as.integer(!is.na(x) & x == "Yes")
clg_dev <- clg_dev |>
  mutate(
    infrastructure_dummy  = flag(Infrastructure),
    distress_dummy        = flag(Financial_Distress),
    covid_dummy           = flag(COVID),
    cofinanced_dummy      = as.integer(Cofinanced == "Yes"),
    interest_free_dummy   = flag(Interest_Free_Loan),
    project_finance_dummy = flag(Project_Finance),
    collateralized_dummy  = flag(Collateralized)
  )

# Map derived dummy names to their codebook source variable
dummy_map <- c(
  infrastructure_dummy  = "Infrastructure",
  distress_dummy        = "Financial_Distress",
  covid_dummy           = "COVID",
  cofinanced_dummy      = "Cofinanced",
  interest_free_dummy   = "Interest_Free_Loan",
  project_finance_dummy = "Project_Finance",
  collateralized_dummy  = "Collateralized"
)

# Wrapper so all regressions inherit codebook + map automatically
reg <- function(...) regress(..., codebook = clg_codebook, var_map = dummy_map)
```

## 1. Loan Size over Time

Does the average loan commitment grow over time?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "Commitment_Year"
)
```

## 2. Infrastructure Premium

Do infrastructure projects receive larger loans than non-infrastructure projects?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "infrastructure_dummy"
)
```

## 3. Concessionality over Time

Is Chinese lending becoming less concessional over time?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "Commitment_Year"
)
```

## 4. Loan Maturity and Infrastructure

Do infrastructure projects carry longer maturities?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Maturity)),
  y_value = "Maturity",
  x_value = "infrastructure_dummy"
)
```

## 5. Interest Rates over Time

Are fixed interest rates rising or falling as China scales up lending?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Fixed_Interest_Rate)),
  y_value = "Fixed_Interest_Rate",
  x_value = "Commitment_Year"
)
```

## 6. COVID and Loan Size

Were loans committed during the COVID period larger or smaller?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "covid_dummy"
)
```

## 7. Co-financing and Loan Size

Are co-financed loans larger than solo Chinese loans?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "cofinanced_dummy"
)
```

## 8. Grace Periods and Infrastructure

Do infrastructure loans come with longer grace periods?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Grace_Period)),
  y_value = "Grace_Period",
  x_value = "infrastructure_dummy"
)
```

## 9. Concessionality and Infrastructure

Are infrastructure loans more or less concessional than non-infrastructure loans?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "infrastructure_dummy"
)
```

## 10. Maturities over Time

Are loan maturities getting longer or shorter as China's program matures?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Maturity)),
  y_value = "Maturity",
  x_value = "Commitment_Year"
)
```

## 11. Interest Rates and Infrastructure

Are infrastructure loans priced differently from non-infrastructure loans?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Fixed_Interest_Rate)),
  y_value = "Fixed_Interest_Rate",
  x_value = "infrastructure_dummy"
)
```

## 12. Interest-Free Loans and Loan Size

Are interest-free loans larger or smaller?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "interest_free_dummy"
)
```

## 13. COVID and Concessionality

Did COVID-era loans carry more favorable terms?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "covid_dummy"
)
```

## 14. Project Finance and Loan Size

Are project-financed deals larger than standard loans?

```{r}
#| results: asis
#| fig-width: 7
#| fig-height: 3
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "project_finance_dummy"
)
```
