---
title: "Analysis"
execute:
  echo: false
  cache: true
fig-width: 9
fig-height: 3.5
---

<style>
.panel-tabset { max-width: 1240px; }
</style>

```{r}
#| include: false
#| cache: false
Sys.setenv(RETICULATE_PYTHON = "/Library/Frameworks/Python.framework/Versions/3.12/bin/python3")
```

```{python}
#| label: polygon-map
#| cache: true
import json, pathlib
from collections import defaultdict
import geopandas as gpd
import folium
from branca.element import Element

GPKG = pathlib.Path("../../datasets/aid_data_geospatial.gpkg")

AFRICA_ISO = {
    "DZA","AGO","BEN","BWA","BFA","BDI","CPV","CMR","CAF","TCD","COM","COD",
    "COG","CIV","DJI","EGY","GNQ","ERI","SWZ","ETH","GAB","GMB","GHA","GIN",
    "GNB","KEN","LSO","LBR","LBY","MDG","MWI","MLI","MRT","MUS","MAR","MOZ",
    "NAM","NER","NGA","RWA","STP","SEN","SLE","SOM","ZAF","SSD","SDN","TZA",
    "TGO","TUN","UGA","ZMB","ZWE",
}

gdf = gpd.read_file(GPKG)
africa = gdf[gdf["Recipient.ISO-3"].isin(AFRICA_ISO)].copy()
africa["geometry"] = africa["geometry"].simplify(tolerance=0.05, preserve_topology=True)
africa = africa.to_crs(epsg=4326)

by_year = defaultdict(list)
for _, row in africa.iterrows():
    year = row["Commitment.Year"]
    if year != year:
        continue
    by_year[int(year)].append({
        "type": "Feature",
        "geometry": row["geometry"].__geo_interface__,
        "properties": {
            "Title":     row["Title"],
            "Recipient": row["Recipient"],
            "Sector":    row["Sector.Name"],
            "Amount":    row["Amount.(Constant.USD.2021)"],
            "Year":      int(year),
        },
    })

min_year = min(by_year)
max_year = max(by_year)

m = folium.Map(location=[5, 20], zoom_start=3, tiles="CartoDB positron")
map_var = m.get_name()

slider_element = Element(f"""
<div id="slider-box" style="
    position: fixed; bottom: 16px; left: 50%; transform: translateX(-50%);
    background: #F5F5F5; color: #2E3440;
    font-family: 'Source Sans Pro', Arial, sans-serif;
    padding: 6px 16px 7px; border-radius: 5px; z-index: 9999;
    border: 1px solid #E0E0E0;
    box-shadow: 0 1px 4px rgba(0,0,0,0.10); text-align: center;">
  <span id="year-label" style="font-size:12px; font-weight:600; color:#4C566A; margin-right:10px; letter-spacing:0.04em;">{min_year}</span>
  <input id="year-slider" type="range"
         min="{min_year}" max="{max_year}" value="{min_year}" step="1"
         style="width: 180px; cursor: pointer; vertical-align: middle; accent-color: #C0392B;">
</div>
<script>
window.addEventListener("load", function () {{
  var yearData = {json.dumps(dict(by_year))};
  var map = window["{map_var}"];
  var loaded = {{}};
  var style = {{fillColor:"#c0392b",color:"#922b21",weight:0.5,fillOpacity:0.35}};
  function onEach(f, layer) {{
    var p = f.properties;
    layer.bindTooltip(
      "<b>" + (p.Title||"") + "</b><br>Recipient: " + (p.Recipient||"") +
      "<br>Sector: " + (p.Sector||"") +
      "<br>Amount (USD 2021): " + (p.Amount ? "$"+p.Amount.toLocaleString() : "N/A") +
      "<br>Year: " + p.Year
    );
  }}
  function showUpTo(year) {{
    for (var y = {min_year}; y <= year; y++) {{
      if (!loaded[y] && yearData[y]) {{
        loaded[y] = L.geoJSON(
          {{type:"FeatureCollection",features:yearData[y]}},
          {{style:style,onEachFeature:onEach}}
        ).addTo(map);
      }}
    }}
    Object.keys(loaded).forEach(function(y) {{
      if (parseInt(y) > year) {{ map.removeLayer(loaded[y]); delete loaded[y]; }}
    }});
    document.getElementById("year-label").textContent = year;
  }}
  showUpTo({min_year});
  document.getElementById("year-slider").addEventListener("input", function() {{
    showUpTo(parseInt(this.value));
  }});
}});
</script>
""")

_ = m.get_root().html.add_child(slider_element)
m.save("chinadev_map.html")
```

```{r}
#| label: polygon-map-render
#| cache: false
htmltools::tagList(
  htmltools::tags$iframe(src="chinadev_map.html", width="100%", height="700px",
                         style="border:none; display:block;"),
  htmltools::tags$div(style = "height: 2.5rem;")
)
```

```{r}
#| include: false
library(targets)
library(here)
library(dplyr)
library(ggplot2)
library(tidyr)
library(sandwich)

source(here("analysis", "R", "regress.R"))

tar_config_set(store = here("_targets"))
tar_load(clg_dev)
tar_load(clg_codebook)

# Derived variables (NA treated as 0 for binary indicators)
flag <- function(x) as.integer(!is.na(x) & x == "Yes")
clg_dev <- clg_dev |>
  mutate(
    infrastructure_dummy  = flag(Infrastructure),
    distress_dummy        = flag(Financial_Distress),
    covid_dummy           = flag(COVID),
    cofinanced_dummy      = as.integer(Cofinanced == "Yes"),
    interest_free_dummy   = flag(Interest_Free_Loan),
    project_finance_dummy = flag(Project_Finance),
    collateralized_dummy  = flag(Collateralized)
  )

# Map derived dummy names to their codebook source variable
dummy_map <- c(
  infrastructure_dummy  = "Infrastructure",
  distress_dummy        = "Financial_Distress",
  covid_dummy           = "COVID",
  cofinanced_dummy      = "Cofinanced",
  interest_free_dummy   = "Interest_Free_Loan",
  project_finance_dummy = "Project_Finance",
  collateralized_dummy  = "Collateralized"
)

# Wrapper so all regressions inherit codebook + map automatically
reg <- function(...) regress(..., codebook = clg_codebook, var_map = dummy_map)
```

## 1. Loan Size over Time

Does the average loan commitment grow over time?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "Commitment_Year"
)
```

## 2. Infrastructure Premium

Do infrastructure projects receive larger loans than non-infrastructure projects?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "infrastructure_dummy"
)
```

## 3. Concessionality over Time

Is Chinese lending becoming less concessional over time?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "Commitment_Year"
)
```

## 4. Loan Maturity and Infrastructure

Do infrastructure projects carry longer maturities?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Maturity)),
  y_value = "Maturity",
  x_value = "infrastructure_dummy"
)
```

## 5. Interest Rates over Time

Are fixed interest rates rising or falling as China scales up lending?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Fixed_Interest_Rate)),
  y_value = "Fixed_Interest_Rate",
  x_value = "Commitment_Year"
)
```

## 6. COVID and Loan Size

Were loans committed during the COVID period larger or smaller?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "covid_dummy"
)
```

## 7. Co-financing and Loan Size

Are co-financed loans larger than solo Chinese loans?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "cofinanced_dummy"
)
```

## 8. Grace Periods and Infrastructure

Do infrastructure loans come with longer grace periods?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Grace_Period)),
  y_value = "Grace_Period",
  x_value = "infrastructure_dummy"
)
```

## 9. Concessionality and Infrastructure

Are infrastructure loans more or less concessional than non-infrastructure loans?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "infrastructure_dummy"
)
```

## 10. Maturities over Time

Are loan maturities getting longer or shorter as China's program matures?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Maturity)),
  y_value = "Maturity",
  x_value = "Commitment_Year"
)
```

## 11. Interest Rates and Infrastructure

Are infrastructure loans priced differently from non-infrastructure loans?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Fixed_Interest_Rate)),
  y_value = "Fixed_Interest_Rate",
  x_value = "infrastructure_dummy"
)
```

## 12. Interest-Free Loans and Loan Size

Are interest-free loans larger or smaller?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "interest_free_dummy"
)
```

## 13. COVID and Concessionality

Did COVID-era loans carry more favorable terms?

```{r}
#| results: asis
reg(
  data    = clg_dev |> filter(!is.na(Grant_Element_IMF)),
  y_value = "Grant_Element_IMF",
  x_value = "covid_dummy"
)
```

## 14. Project Finance and Loan Size

Are project-financed deals larger than standard loans?

```{r}
#| results: asis
reg(
  data    = clg_dev,
  y_value = "Amount_Constant_USD_2023",
  x_value = "project_finance_dummy"
)
```
